PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd

```{r neurological frequencies alsfrs.limb_weakness_noticed_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.limb_weakness_noticed_past)) %>%
  count(covid_test_positive, alsfrs.limb_weakness_noticed_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.normal}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.normal)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.normal) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.slow_or_sloppy_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.slow_or_sloppy_all_words_are_legible)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.not_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.not_all_words_are_legible)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.not_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.able_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.able_to_grip_pen)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.able_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.unable_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.unable_to_grip_pen)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.unable_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.have_you_noticed_any_difficulty_walking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.have_you_noticed_any_difficulty_walking)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.have_you_noticed_any_difficulty_walking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.do_you_have_any_difficulty_climbing_stairs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(alsfrs.do_you_have_any_difficulty_climbing_stairs)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("ess"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies ess.felt_excessively_sleepy_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.felt_excessively_sleepy_past)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.felt_excessively_sleepy_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_reading}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_and_reading)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_and_reading) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.watching_tv}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.watching_tv)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.watching_tv) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_inactive_in_a_public_place}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_inactive_in_a_public_place)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_inactive_in_a_public_place) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.break_passenger_car_hour}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.break_passenger_car_hour)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.break_passenger_car_hour) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.afternoon_rest_circumstances_lying}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.afternoon_rest_circumstances_lying)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.afternoon_rest_circumstances_lying) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_talking_to_someone}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_and_talking_to_someone)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_and_talking_to_someone) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_quietly_after_a_lunch_without_alcohol}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sitting_quietly_after_a_lunch_without_alcohol)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.car_minutes_stopped_traffic}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.car_minutes_stopped_traffic)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.car_minutes_stopped_traffic) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.insomnia}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.insomnia)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.insomnia) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.narcolepsy}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.narcolepsy)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.narcolepsy) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.rem_sleep_behaviour_disorder}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.rem_sleep_behaviour_disorder)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.rem_sleep_behaviour_disorder) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.restless_legs_syndrome}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.restless_legs_syndrome)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.restless_legs_syndrome) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_apnea}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sleep_apnea)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sleep_apnea) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_terrors}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sleep_terrors)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sleep_terrors) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleepwalking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.sleepwalking)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.sleepwalking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.other}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.other)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.other) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.none}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(ess.none)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, ess.none) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  group_by(covid_test_positive) %>%
  select(
    starts_with("midas"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies midas.headaches_suffered_past_month}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.headaches_suffered_past_month)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.headaches_suffered_past_month) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_miss_work_school}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.days_past_month_miss_work_school)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.days_past_month_miss_work_school) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_work_school_half_productivity}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.days_past_month_work_school_half_productivity)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.days_past_month_work_school_half_productivity) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_miss_housework}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.days_past_month_miss_housework)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.days_past_month_miss_housework) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_housework_half_productivity}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.days_past_month_housework_half_productivity)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.days_past_month_housework_half_productivity) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_miss_social_activities}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_test_positive)) %>%
  filter(!is.na(midas.days_past_month_miss_social_activities)) %>%
  group_by(covid_test_positive) %>%
  count(covid_test_positive, midas.days_past_month_miss_social_activities) %>%
  mutate(Prop = round(n/sum(n), 2))
```

>>>>

```{r neurological frequencies alsfrs.limb_weakness_noticed_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.limb_weakness_noticed_past)) %>%
  count(covid_probable_case_incl_screening, alsfrs.limb_weakness_noticed_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.normal}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.normal)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.normal) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.slow_or_sloppy_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.slow_or_sloppy_all_words_are_legible)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.not_all_words_are_legible}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.not_all_words_are_legible)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.not_all_words_are_legible) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.able_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.able_to_grip_pen)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.able_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.unable_to_grip_pen}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.unable_to_grip_pen)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.unable_to_grip_pen) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.have_you_noticed_any_difficulty_walking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.have_you_noticed_any_difficulty_walking)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.have_you_noticed_any_difficulty_walking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies alsfrs.do_you_have_any_difficulty_climbing_stairs}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(alsfrs.do_you_have_any_difficulty_climbing_stairs)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("ess"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies ess.felt_excessively_sleepy_past}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.felt_excessively_sleepy_past)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.felt_excessively_sleepy_past) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_reading}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_and_reading)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_and_reading) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.watching_tv}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.watching_tv)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.watching_tv) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_inactive_in_a_public_place}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_inactive_in_a_public_place)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_inactive_in_a_public_place) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.break_passenger_car_hour}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.break_passenger_car_hour)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.break_passenger_car_hour) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.afternoon_rest_circumstances_lying}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.afternoon_rest_circumstances_lying)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.afternoon_rest_circumstances_lying) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_and_talking_to_someone}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_and_talking_to_someone)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_and_talking_to_someone) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sitting_quietly_after_a_lunch_without_alcohol}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sitting_quietly_after_a_lunch_without_alcohol)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.car_minutes_stopped_traffic}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.car_minutes_stopped_traffic)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.car_minutes_stopped_traffic) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.insomnia}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.insomnia)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.insomnia) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.narcolepsy}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.narcolepsy)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.narcolepsy) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.rem_sleep_behaviour_disorder}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.rem_sleep_behaviour_disorder)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.rem_sleep_behaviour_disorder) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.restless_legs_syndrome}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.restless_legs_syndrome)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.restless_legs_syndrome) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_apnea}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sleep_apnea)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sleep_apnea) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleep_terrors}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sleep_terrors)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sleep_terrors) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.sleepwalking}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.sleepwalking)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.sleepwalking) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.other}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.other)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.other) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies ess.none}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.none)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.none) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  select(
    starts_with("midas"),
    -ends_with("numeric")
  ) %>% 
  colnames()
```

```{r neurological frequencies midas.headaches_suffered_past_month}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(midas.headaches_suffered_past_month)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, midas.headaches_suffered_past_month) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_miss_work_school}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(midas.days_past_month_miss_work_school)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, midas.days_past_month_miss_work_school) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_work_school_half_productivity}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(midas.days_past_month_work_school_half_productivity)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, midas.days_past_month_work_school_half_productivity) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_miss_housework}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(midas.days_past_month_miss_housework)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, midas.days_past_month_miss_housework) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_housework_half_productivity}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(midas.days_past_month_housework_half_productivity)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, midas.days_past_month_housework_half_productivity) %>%
  mutate(Prop = round(n/sum(n), 2))
```

```{r neurological frequencies midas.days_past_month_miss_social_activities}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(midas.days_past_month_miss_social_activities)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, midas.days_past_month_miss_social_activities) %>%
  mutate(Prop = round(n/sum(n), 2))
```
